---
title: "LMwithPred"
author: "Brooke De La Torre"
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
```

## Introduction
We are using a linear model to predict a stimulated strength score based on arm strength and or grip strength. 

```{r}
data <- read.csv(file="http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)    
```
```{r}
dataF <- read.csv(file="http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)    
```

##model1

Scatterplot SIMS is a function of ARM
```{r}
plot(SIMS~ARM, data=dataF)
```

##Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(dataF,aes(y=SIMS,x=ARM))
```

##Now add in scatterplot

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```

```{r}
model.1=lm(SIMS~ARM,data=dataF)
summary.lm(model.1)
```
This is a linear model of SIMS based on ARM strength. The adjusted rsquare is equal to 8.467

##model2

Scatterplot SIMS is a function of GRIP
```{r}
plot(SIMS~GRIP, data=dataF)
```

##Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(dataF,aes(y=SIMS,x=GRIP))
```

##Now add in scatterplot

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```

```{r}
model.2=lm(SIMS~GRIP,data=dataF)
summary.lm(model.2)
```